### 2017-12-24 papers/cua.tex
cua: add send rights in messages and line up tick marks correctly again

\usepackage{tikz}
\usetikzlibrary{positioning, fit}

@@

\tikzstyle{task} = [draw, fill=blue!20, text width=8em, text depth=8em, text centered,
  minimum width=10em, minimum height=10em, rounded corners]

\tikzstyle{message} = [draw, fill=red!20, text width=5em, text depth=2em, text centered,
  minimum width=5em, minimum height=2em, rounded corners]

\newcommand\task[4]{
\node (#1) [matrix, task] at (#2) {\node {#1}; #4

\IfSubStr{#3}{l}{
\foreach \i in {-8,...,8}%
{
  \draw[xshift=-5em, ultra thick] (0,0.2 * \i) -- (0.2,0.2 * \i) coordinate (#1 Port \i);

}
}{}

\IfSubStr{#3}{r}{
\foreach \i in {-8,...,8}%
{
  \draw[xshift=5em, ultra thick] (-0.2,0.2 * \i) -- (0,0.2 * \i) coordinate (#1 Port \i);

}
}{}

@@

\begin{center}
\begin{tikzpicture}

\task{Task 1}{0,0}{r}{
\node (message1) [message] {Message 1};
}
\task{Task 2}{15 em,0}{l}{
\node (message2) [message] {Message 1};
\node (message2a) [message] at (1 em, -2 em) {Message 2};
}
\task{Task 3}{0,-15 em}{r}{
\node (message3) [message] {Message 2};
}

>>>>

\usepackage{tikz}
\usetikzlibrary{positioning, fit, backgrounds}

@@

\tikzstyle{task} = [draw, fill=blue!20, rounded corners]

\tikzstyle{message} = [draw, fill=red!20, text width=5em, text depth=3em, text centered,
  minimum width=5em, minimum height=2em, rounded corners]

\newcommand\task[4]{
\matrix (#1) [task, inner xsep=0] at (#2) { \node {#1}; \\ #4

% print port tick marks in fill color if they are disabled, in order to make
% them expand out the dimensions of the task box

\foreach \i in {-8,...,8}
{
\IfSubStr{#3}{l}{
  \draw[xshift=-5em, ultra thick] (0,0.2 * \i) -- (0.2,0.2 * \i) coordinate (#1 Port \i);
}{
  \draw[xshift=-5em, ultra thick, color=blue!20] (0,0.2 * \i) -- (0.2,0.2 * \i) coordinate;
}
\IfSubStr{#3}{r}{
  \draw[xshift=5em, ultra thick] (-0.2,0.2 * \i) -- (0,0.2 * \i) coordinate (#1 Port \i);
}{
  \draw[xshift=5em, ultra thick, color=blue!20] (-0.2,0.2 * \i) -- (0,0.2 * \i) coordinate;
}
}

@@

\begin{center}

\begin{tikzpicture}

\task{Task 1}{0,0}{r}{
% print two sendright nodes, one to fill the message1 box to the correct size,
% and another one to actually draw it, since message1 will overwrite the
% first sendright
\node (sendright) [draw, fill=orange] {Send 41};
\node (message1) [fit=(sendright), message] {Message 1};
\node (sendright) [draw, fill=orange] {Send 41};
}
\task{Task 2}{15 em,0}{l}{
\node (message2) [message] {Message 1};
\node (message2a) [message] at (1 em, -2 em) {Message 2};
}
\task{Task 3}{0,-15 em}{r}{
\node (message3) [message] {Message 2};
}
